Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-10 paper/disc20clustering.tex
Comments
Distributed

\maciek{"this means," "\textbf{this means that}"}

@@

Although we have described our algorithms globally so far, we note that these allow for efficient distributed implementations. 
The algorithm PPL from Section~\ref{sec:ppl} can be distributed
similarly to the approach in~\cite{sigmetrics19_partitioning}.
The algorithm for $k=2$ from Section~\ref{sec:k2} performs only local communication for each request: counters are kept on the clusters and updated locally, and each migration concerns only two clusters.
Furthermore, we proposed an efficient distributed implementation of the algorithm for $k=3$ in Section~\ref{sec:k3}.

>>>>

@@

Although we have described our algorithms globally so far, we note that these allow for efficient distributed implementations. 
The algorithm PPL from Section~\ref{sec:ppl} can be distributed
similarly to the approach in~\cite{sigmetrics19_partitioning}.
The algorithm for $k=2$ from Section~\ref{sec:k2} performs only local communication for each request: counters are kept on the clusters and updated locally, and each migration is local within two clusters that reached the collocation threshold $\lambda$.
Furthermore, we proposed an efficient distributed implementation of the algorithm for $k=3$ in Section~\ref{sec:k3}.
